### 2021-06-26 code/manuscript.Rmd
Fix Bayesian model outputs

```{r setup, include=FALSE}
# Load packages
library(MASS)
library(lme4)
library(buildmer)
library(emmeans)
library(brms)
library(parallel)
library(reticulate)
library(magick)
library(papaja)
library(cowplot)
library(scales)
library(tidyverse)
library(magrittr)

@@

# File names for easier I/O
fnames <- list(
  montage = "results/montage.csv",
  objects_per_condition = "results/obj-per-cond.csv",
  ave_grand = "results/ave_grand.csv",
  ave_tfr_flat = "results/ave-tfr_flat.csv",
  ave_tfr_diff = "results/ave-tfr_diff.csv",
  models_lme = "results/models_lme.RDS",
  models_brm = paste0("results/model_brm_", c("RT", "P1", "N170", "N400"), ".RDS") %>%
    set_names(c("RT", "P1", "N170", "N400")),
  model_brm_prior = "results/model_brm_prior.RDS"
)
```

@@

```{r models_brm, eval=TRUE}
# Color scheme for plots
bayesplot::color_scheme_set("purple")

@@

# Prior predictive checks for population-level parameters
prior_summary(fit_brm_prior)
summary(fit_brm_prior)
mcmc_plot(fit_brm_prior, "areas", pars = "^b_", prob_outer = 0.95) +
  theme(text = element_text(family = "Helvetica", size = 10))

@@

  # Sample from the posterior distribution
  fit_brm <- update(
    fit_brm_prior,
    formula = formula_dv,
    sample_prior = "yes",
    file = fnames$models_brm[[dv]],
    file_refit = "on_change"
  )

@@

# Posterior predictive checks for population-level parameters
summary(models_brm$P1)
mcmc_plot(models_brm$P1, "areas", pars = "^b_", prob_outer = 0.95) +
  theme(text = element_text(family = "Helvetica", size = 10))

# Posterior predictive checks subject by subject
pp_check(
  models_brm$P1,
  type = "dens_overlay_grouped",
  nsamples = 50,
  group = "subject_id"
)
pp_check(
  models_brm$P1,
  type = "stat_grouped",
  nsamples = 1000,
  group = "subject_id",
  stat = "sd"
)

bf_bayestest <- bayestestR::bayesfactor(models_brm$P1)
bf_bayestest
```

>>>>

```{r setup, include=FALSE}
# Load packages
library(MASS)
library(lme4)
library(buildmer)
library(emmeans)
library(bayesplot)
library(brms)
library(parallel)
library(reticulate)
library(magick)
library(papaja)
library(cowplot)
library(scales)
library(tidyverse)
library(magrittr)

@@

# File names for easier I/O
fnames <- list(
  montage = "results/montage.csv",
  objects_per_condition = "results/obj-per-cond.csv",
  ave_grand = "results/ave_grand.csv",
  ave_tfr_flat = "results/ave-tfr_flat.csv",
  ave_tfr_diff = "results/ave-tfr_diff.csv",
  models_lme = "results/models_lme.RDS",
  models_brm = paste0(
    "results/model_brm_", c("logRT", "P1", "N170", "N400"), ".RDS"
  ) %>%
    set_names(c("logRT", "P1", "N170", "N400")),
  model_brm_prior = "results/model_brm_prior.RDS"
)
```

@@

```{r models_brm, eval=TRUE}
# Theme for plots
bayesplot_theme_update(text = element_text(family = "Helvetica", size = 10))
color_scheme_set("purple")

@@

# Prior predictive checks for population-level parameters
prior_summary(fit_brm_prior)
summary(fit_brm_prior)
mcmc_plot(fit_brm_prior, "areas", pars = "^b_", prob_outer = 0.95)

@@

  # Sample from the posterior distribution
  fit_brm <- update(
    fit_brm_prior,
    formula = formula_dv,
    newdata = trials,
    sample_prior = "yes",
    file = fnames$models_brm[[dv]],
    file_refit = "on_change"
  )

@@

# Posterior predictive checks for population-level parameters
example_model <- models_brm$N400
example_model$summary
example_model$hypotheses
mcmc_plot(example_model$model, "areas", pars = "^b_", prob_outer = 0.95) +
  theme(text = element_text(family = "Helvetica", size = 10))

# Posterior predictive checks subject by subject
pp_check(
  example_model$model,
  type = "dens_overlay_grouped",
  nsamples = 50,
  group = "subject_id"
)
pp_check(
  example_model$model,
  type = "stat_grouped",
  nsamples = 1000,
  group = "subject_id",
  stat = "sd"
)

bf_bayestest <- bayestestR::bayesfactor(example_model$model)
bf_bayestest
```
